---
title: "FDA 503B Product Report"
author: "08/31/2021 v1.0.1"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::gitbook: default
  #bookdown::pdf_book: default
  #bookdown::html_document2: default
---

```{r import_libraries, include=FALSE, echo = FALSE, message=FALSE, cache = FALSE, warning = FALSE}

library(tidyverse)
library(readr)
library(readxl)
library(ggplot2)
library(plotly)

```

```{r import_data, include=FALSE, echo = FALSE, message=FALSE, cache = FALSE}
# Import Facility Information
# facility_info <- read_excel("~/Desktop/FDA-503B/report/data/facility_info.xlsx")
facility_info <- read_excel("./data/facility_info.xlsx")

# Import Geographic data
# geographic_data <- read_excel("~/Desktop/FDA-503B/report/data/geographic_data.xlsx")
geographic_data <- read_excel("./data/geographic_data.xlsx")

# Facility Product Count 
# facility_product_count <- read_csv("~/Desktop/FDA-503B/report/data/facility_product_count.csv")
facility_product_count <- read_csv("./data/facility_product_count.csv")# %>%
   # mutate(Segment = case_when(is.na(Segment) ~ "NA"))

# Product List
# product_list <- read_csv("~/Desktop/FDA-503B/report/data/product_list.csv")
product_list <- read_csv("./data/product_list.csv")

```

```{r custom_functions, include=FALSE, echo = FALSE, message=FALSE, cache = FALSE}

# Reorder size, honestly not sure if this is still being used by anything
# reorder_size <- function(x) {
#   factor(x, levels = names(sort(table(x), decreasing = TRUE)))
# }

segment_graph <- function(a){

  count_dosage <- facility_product_count %>%
    filter(Facility == a) %>%
    select(Active, Dosage, Segment, Facility)
  
  group_segment_facility <- count_dosage %>%
    group_by(Segment, Facility) %>%
    distinct(Active, .keep_all = TRUE) %>%
    mutate(FacilitySegmentCount = n()) %>%
    ungroup() %>%
    select(Facility, Segment, FacilitySegmentCount)

  count_dosage <- count_dosage %>%
    left_join(group_segment_facility, by = c("Facility", "Segment")) %>%
    distinct_all()

  group_dosage_segment <- count_dosage %>%
    group_by(Facility, Segment, Dosage) %>%
    mutate(FacilityDosageCount = n()) %>%
    ungroup() %>%
    select(Facility, Segment, Dosage, FacilityDosageCount) %>%
    distinct_all() 

  count_dosage <- count_dosage %>%
    left_join(group_dosage_segment, by = c("Facility", "Segment", "Dosage")) %>%
    distinct_all() %>% 
    select(-Active, -Facility) %>%
    group_by(Segment) %>%
    arrange(Segment)

  segment_labels <- count_dosage %>%
    distinct(Segment, FacilitySegmentCount)

  ggplot() +
    geom_bar(count_dosage, mapping = aes(x = reorder(Segment, -FacilitySegmentCount), fill = Dosage)) +
    geom_text(segment_labels, mapping = aes(x = reorder(Segment, -FacilitySegmentCount), y = FacilitySegmentCount, label =    FacilitySegmentCount), vjust = -0.5) +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
       axis.text.y = element_blank(), axis.ticks.y = element_blank()) +
    labs(title = paste(a, "Segmentation", sep = " " ), x = element_blank(),
       y = "# of Products in Segment")
  
}

facility_table_1 <- function(a){
  
  facility_table_1 <- product_list %>%
    select(Facility, City, State, InitialRegistration, EstSales, FacilitySqFt, Employees) %>%
    filter(Facility == a) %>%
    distinct(Facility, .keep_all = TRUE) %>%
    knitr::kable() 
  
  facility_table_1
  
}

facility_table_2 <- function(a){
  
    facility_table_2 <- product_list %>%
    select(Facility, EstFacilitySize, ProductCount, Competing, Services, `503A`) %>%
    filter(Facility == a) %>%
    distinct(Facility, .keep_all = TRUE) %>%
    knitr::kable()

  facility_table_2
  
}

segment_desc_ActiveCount <- function(a){
  
  segment_desc_ActiveCount <- facility_product_count %>%
  select(Active, Segment, ActiveCount, ProducedByCP) %>%
  filter(Segment == a) %>%
  distinct(Active, .keep_all = TRUE) %>%
  arrange(desc(ActiveCount)) %>%
  knitr::kable()
  
  segment_desc_ActiveCount
  
}

```

# Data Sources

This data covers the years 2019 and 2020. 

[Segmentation Data](./data/user-formatted/Facility Product Count.xlsx)

This Excel document is focused on products and segments, it contains limited
information on facilities, and is best used in conjunction with this report. Each 
product will appear multiple times within this document, one time for each facility
that produced it, and one time for each segment that it falls into. 

By using the Excel filter functions of each column you can refine the data you
are looking at to see which products are in each segment, products that are produced
by a single facility, and what products facilities are producing. This report acts
as a supplement to this document, presenting information from other sets of data 
to enable product related decision making. 

Column               | Description
-------------------- | -------------
Active               | Active Ingredient
Facility             | Registered 503B Facility name
Segment              | Dental, Dermatology, InfusionTherapy, Nutraceuticals, Optical, Other, PlasticSurgery, Surgical
ActiveCount          | Number of times Active was reported as produced
ProductCount         | Number of products Facility produces across segments
FacilitySegmentCount | Number of products Facility produces within Segment
SegmentCount         | Number of products within Segment
ProducedByCP         | Y/NA Has the Active ever been produced by RAM/Compound Preferred?

[FDA 503B Product List](./data/user-formatted/Raw FDA Data.xlsx)

This document contains unmodified data directly from the FDA in a useful Excel
format. 

Column                  | Description
----------------------- | -------------
Active Ingredients      | Active ingredients in product
Active Ingredients Info | Concentration of Active  
Dosage                  | Reported dosage form
Estab. Name             | Registered 503B Facility name
Package Description     | Description of package
NDC Package Code        | Unique packaging identifier
Report Year             | Year and 6 month period in which Active was produced


[Facility Information](./data/facility_info.xlsx)

The information in this document can be found summarized in this report under
facility information summaries. The document contains information on each 503B
facility that reported production in the years of 2019 and 2020. 

Column               | Description
-------------------- | -------------
Facility             | Registered 503B Facility name
UID                  | FDA Unique Identifier 
City                 | City Facility Location
Longitude            | Geolocation
Latitude             | Geolocation
InitialRegistration  | Initial registration as an FDA 503B facility
FacilitySqFt         | Estimated facility square footage, estimates are based on Google Map imagery 
Employees            | Dun & Bradstreet 2021 employee estimate
Services             | Services offered by Facility
EstSales             | Dun & Bradstreet 2021 sales estimate
EstFacilitySize      | Facility size estimate, based on SqFt, EmployeeEst, and EstSales

[Geographic Data](./data/geographic_data.xlsx)

This document contains specific information about the states in which some facilities 
can distribute compounded products. This information is mostly useful in graphic form. 

Column               | Description
-------------------- | -------------
Facility             | Registered 503B Facility name
Longitude            | Geolocation
Latitude             | Geolocation
Territory            | Facility territory, list of US states in which the facility can deliver products

# Facility Information Example 

## RAM Pharma, Inc.

### Table 1

Each 503B facility entry contains similar information. The first table contains
information on location, registration, and some key information about facility
size, sales estimates, and a head count estimate. 

Sales and head count are derived from the Dun & Bradstreet company database, 
unless specific information about head count was available on a facilities 
website. Square footage was estimated based on Google Maps images. 

```{r ram_facility_info_1, include = TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%"}

x <- "RAM Pharma, Inc."

facility_table_1(x)
  
```

### Table 2

The second table contains information including a facility size estimate, 
product specific information, and services offered. The column Product count represents the number of unique products reported by a facility in the years 
of 2019 and 2020. The column Competing is the number of those products that RAM/Compound Preferred has produced and reported in the past. 

```{r ram_facility_info_2, include = TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%"}
  
x <- "RAM Pharma, Inc."

facility_table_2(x)

```

### Segment Chart

The final graph that will appear on each facility page is a segmentation bar chart. 
This chart shows the number of products in each facilities product mix that fall
into a particular segment. 

For example, BLT Cream is categorized into two segments, Dental and PlasticSurgery.
In the chart below, BLT Cream will be counted twice, once in Dental and once in 
PlasticSurgery. 

If we wanted to know exactly which products made up the the PlasticSurgery 
segment for RAM, we could use the [Segmentation Data](./data/user-formatted/Facility Product Count.xlsx) Excel document. 

```{r ram_facility_info_3, include = TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning=FALSE}
# Segment Graph RAM Pharma

x <- "RAM Pharma, Inc."

segment_graph(x)

```

# Facility Information Summaries

## General Summaries

### Segments Bar Graph

```{r segments_bar, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%"}

facility_product_count %>%
  filter(Segment != "NA") %>%
  select(Segment, SegmentCount) %>%
  distinct(Segment, .keep_all = TRUE) %>%
  mutate(SegmentCount = as.numeric(SegmentCount)) %>%
  ggplot(aes(x = reorder(Segment, -SegmentCount), y = SegmentCount)) +
  geom_bar(stat = "identity") +
  theme_classic() +
    geom_text(aes(label = SegmentCount), vjust = -0.5) +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.text.y = element_blank(), axis.ticks.y = element_blank()) +
    labs(title = "Products in Segment", x = element_blank(), 
         y = "# of Products in Segment")

```

### 503B Facilities Geographic Distribution

```{r geographic_facility_info, include = TRUE, echo = FALSE, message=FALSE, cache = TRUE, warning = FALSE, out.width="100%"}

df <- facility_info

g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showland = TRUE,
  landcolor = toRGB("gray95"),
  subunitcolor = toRGB("gray85"),
  countrycolor = toRGB("gray85"),
  countrywidth = 0.5,
  subunitwidth = 0.5
)

fig <- plot_geo(df, lat = ~lat, lon = ~lon)
fig <- fig %>% add_markers(
  text = ~paste(Facility, City, State, EstFacilitySize, sep = "<br />"),
  color =  ~EstFacilitySize, symbol = I("square"), size = I(8), 
  hoverinfo = "text"
)

fig <- fig %>% layout(
  title = 'Geographic Distribution of 503B Facilities (Hover for name)', geo = g
)

fig


```

## Facilities

### AnazaoHealth Corporation

```{r anazao_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "AnazaoHealth Corporation"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Apollo Care, LLC

```{r apollo_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Apollo Care, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### ASP Cares

```{r asp_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "ASP Cares"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Athenex Pharma Solutions, LLC

```{r athenex_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Athenex Pharma Solutions, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Atlas Pharmaceuticals, LLC

```{r atlas_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Atlas Pharmaceuticals, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Auro Pharmacies, Inc

```{r auro_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Auro Pharmacies, Inc"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Avella of Deer Valley, Inc. #38

```{r avella_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Avella of Deer Valley, Inc. #38"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

<!-- ### BayCare Integrated Service Center, LLC dba BayCare Central Pharmacy -->

<!-- ```{r baycare_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE} -->

<!-- x <- "BayCare Integrated Service Center, LLC dba BayCare Central Pharmacy" -->

<!-- facility_table_1(x) -->
<!-- facility_table_2(x) -->

<!-- segment_graph(x) -->

<!-- ``` -->

### BPI Labs LLC

```{r BPI_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "BPI Labs LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Brookfield Medical Surgical Supply

```{r brookfield_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Brookfield Medical Surgical Supply"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### BSO, LLC

```{r bso_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "BSO, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Central Admixture Pharmacy Services, Inc.

```{r central_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Central Admixture Pharmacy Services, Inc."

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Complete Pharmacy and Medical Solutions

```{r complete_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Complete Pharmacy and Medical Solutions"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Denver Solutions, LLC dba Leiters Health

```{r denver_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Denver Solutions, LLC dba Leiters Health"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Eagle Pharmacy, Inc.

```{r eagle_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Eagle Pharmacy, Inc."

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Edge Pharmacy Services LLC

```{r edge_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Edge Pharmacy Services LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Empower Pharmacy

```{r empower_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Empower Pharmacy"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Exela Pharma Sciences, LLC.

```{r exela_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Exela Pharma Sciences, LLC."

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Fagron Compounding Services LLC dba Fagron Sterile Services LLC

```{r fagron_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Fagron Compounding Services LLC dba Fagron Sterile Services LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### F. H. Investments. Inc. DBA Asteria Health

```{r fh_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "F. H. Investments. Inc. DBA Asteria Health"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### FARMAKEIO OUTSOURCING LLC

```{r farmakeio_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "FARMAKEIO OUTSOURCING LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Fresenius Kabi Compounding, LLC

```{r fresenius_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Fresenius Kabi Compounding, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Fusion IV Pharmaceuticals, Inc. dba Axia Pharmaceuticals

```{r fusion_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Fusion IV Pharmaceuticals, Inc. dba Axia Pharmaceuticals"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Hybrid Pharma

```{r hybrid_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Hybrid Pharma"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Imprimis NJOF, LLC

```{r imprimis_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Imprimis NJOF, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### IntegraDose Compounding Services, LLC

```{r integradose_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "IntegraDose Compounding Services, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### JCB Laboratories LLC

```{r jcb_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "JCB Laboratories LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### KRS Global Biotechnology, Inc.

```{r krs_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "KRS Global Biotechnology, Inc."

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### LEESAR INC

```{r leesar_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "LEESAR INC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Leiter's Compounding

```{r leiters_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Leiter's Compounding"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Medi-Fare Drug

```{r medifare_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Medi-Fare Drug"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### MedisourceRx

```{r mediasource_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "MedisourceRx"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Nephron Sterile Compounding Center, LLC

```{r nephron_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Nephron Sterile Compounding Center, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### New England Life Care LLC dba Advanced Compounding Solutions

```{r newengland_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "New England Life Care LLC dba Advanced Compounding Solutions"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Nubratori, Inc

```{r nubratori_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Nubratori, Inc"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### OLYMPIA PHARMACY

```{r olympia_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "OLYMPIA PHARMACY"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Optum Compounding Services, LLC

```{r optum_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Optum Compounding Services, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### OurPharma LLC

```{r outpharma_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "OurPharma LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Pacifico National, Inc.  dba AmEx Pharmacy

```{r pacifico_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Pacifico National, Inc.  dba AmEx Pharmacy"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Pentec Health, Inc

```{r pentec_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Pentec Health, Inc"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

<!-- ### Pantheon Labs LLC -->

<!-- ```{r pantheon_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE} -->

<!-- x <- "Pantheon Labs LLC" -->

<!-- facility_table_1(x) -->
<!-- facility_table_2(x) -->

<!-- segment_graph(x) -->

<!-- ``` -->

### Pharmaceutic Labs, LLC

```{r pharmaceutic_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Pharmaceutic Labs, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### PharMEDium Services, LLC SugarLand

```{r pharmedsugarland_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "PharMEDium Services, LLC SugarLand"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Pharmedium Services, LLC, Dayton

```{r pharmeddayton_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Pharmedium Services, LLC, Dayton"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Pharmedium Services, LLC Cleveland

```{r pharmedcleveland_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Pharmedium Services, LLC Cleveland"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Pine Pharmaceuticals LLC

```{r pine_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Pine Pharmaceuticals LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Premier Pharmacy Labs, Inc

```{r premier_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Premier Pharmacy Labs, Inc"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Qualgen LLC

```{r qualgen_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Qualgen LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### QuVa Pharma, Inc.

```{r quva_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "QuVa Pharma, Inc."

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### RC Outsourcing, LLC

```{r rc_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "RC Outsourcing, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Right Value Drug Stores llc dba Carie Boyd's Prescription Shop

```{r rightval_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Right Value Drug Stores llc dba Carie Boyd's Prescription Shop"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### RXQ Compounding, LLC

```{r rxq_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "RXQ Compounding, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### SCA Pharmaceuticals, LLC

```{r sca_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "SCA Pharmaceuticals, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Sincerus Florida, LLC

```{r sincerus_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Sincerus Florida, LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Ssm Hlth St Clare Hosp-Fnton

```{r ssm_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Ssm Hlth St Clare Hosp-Fnton"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

<!-- ### STAQ Pharma -->

<!-- ```{r staq_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE} -->

<!-- x <- "STAQ Pharma" -->

<!-- facility_table_1(x) -->
<!-- facility_table_2(x) -->

<!-- segment_graph(x) -->

<!-- ``` -->

### SterRx

```{r sterrx_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "SterRx"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Stokes Healthcare

```{r stokes_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Stokes Healthcare"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### US Compounding, Inc.

```{r uscomp_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "US Compounding, Inc."

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### US Specialty Formulations LLC

```{r usspec_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "US Specialty Formulations LLC"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Wells Pharmacy, Inc

```{r wells_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Wells Pharmacy, Inc"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

### Wells Pharma of Houston

```{r wellshout_facility_info, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

x <- "Wells Pharma of Houston"

facility_table_1(x)
facility_table_2(x)

segment_graph(x)

```

## Lists

### Dental

```{r descending_1, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

segment_desc_ActiveCount("Dental")

```

### Dermatology

```{r descending_2, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

segment_desc_ActiveCount("Dermatology")
```

### InfusionTherapy

```{r descending_3, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

segment_desc_ActiveCount("InfusionTherapy")

```

### Nutraceuticals

```{r descending_4, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

segment_desc_ActiveCount("Nutraceuticals")

```

### Optical

```{r descending_5, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

segment_desc_ActiveCount("Optical")

```

### Surgical

```{r descending_7, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

segment_desc_ActiveCount("Surgical")

```

### PlasticSurgery

```{r descending_8, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

segment_desc_ActiveCount("PlasticSurgery")

```

### Other

```{r descending_6, include-TRUE, echo = FALSE, message=FALSE, cache = FALSE, out.width="100%", warning = FALSE}

segment_desc_ActiveCount("Other")

```
